\Large \bf Dark Decoys: Conjuring Proxies from Unused Address Space

### 2019-02-06 paper/paper.tex
parskip bullshit, add tls 1.3 section and address utilization

% to be able to draw some self-contained figs
\usepackage{tikz}
\usepackage{amsmath}

@@

Inside the message, the client communicates a random \textbf{seed}, and other
configuration-specific information, such as flags to signify version, feature
support, and which set of dark decoy network prefixes the client knows of. The
client and server use a hash of the provided seed to determine which specific
dark decoy IP address to register. It may seem intuitive to instead have the client
send the specific IP address to register, but allowing the client arbitrary
choice also allows censors to register suspected dark decoys and block them if
they pick up. By using a hash, the censor would have to pre-image the hash to
obtain a seed it could use to register for a desired IP address. It also gives a
secret (the seed) that only the client and station know, even after the client
connects to the dark decoy address.

% Note on IPv6 space? /32 of IPv6 is 96-bits to select...
We note that IP addresses are selected from unused but still routed address
space that passes by the ISP. Traffic to unrouted addresses would produce ICMP
responses that a censor could observe, and are also easily blocked with knowledge
of a routing table. Because we support the use of IPv6 addresses, censors will
also be unable to scan ahead of time to determine if the host has been there
previously, or what was there before. While they can probe suspected dark decoy
addresses after clients connect to them, at that point the address has already been
registered, preventing the censor from identifying differences in behavior
before and after registration.

@@

@@

@@

\paragraph{Mask Site Selection}
How do we get the list of masked sites? Alexa list? passive observation?

@@

TLS~1.3....

%-Registration
%-Dark decoy selection (seed -> IP)
%-Connection to Dark Decoy Application (DD App)
%-IPv6 vs IPv4 dark decoys

>>>>

% to be able to draw some self-contained figs
\usepackage{tikz}
%\usepackage{parskip}
\usepackage{amsmath}
%\setlength{\parskip}{1pt} % 1ex plus 0.5ex minus 0.2ex}
\setlength\parskip{1pt}
\include{figures}

@@

Inside the message, the client communicates a random \textbf{seed}, and other
configuration-specific information, such as flags to signify version, feature
support, and which set of dark decoy network prefixes the client knows of. The
client and server use a hash of the provided seed to determine which specific
dark decoy IP address to register. It may seem intuitive to instead have the client
send the specific IP address to register, but allowing the client arbitrary
choice also allows the censor to register suspected dark decoys and block them if
they pick up. By using a hash, the censor would have to pre-image the hash to
obtain a seed it could use to register for a desired IP address. It also gives a
secret (the seed) that only the client and station know, even after the client
connects to the dark decoy address.

@@

%-IPv6 vs IPv4 dark decoys subsection?

\subsection{Address utilization}

% Note on IPv6 space? /32 of IPv6 is 96-bits to select...
Dark decoy IP addresses are selected from unused but still routed address
space that passes by the ISP. Traffic to unrouted addresses would produce ICMP
responses that a censor could observe, and are also easily blocked with knowledge
of a routing table. Because we support the use of IPv6 addresses, censors will
also be unable to scan ahead of time to determine if the host has been there
previously, or what was there before. While they can probe suspected dark decoy
addresses after clients connect to them, at that point the address has already been
registered, preventing the censor from identifying differences in behavior
before and after registration.

While address utilization in IPv4 is quite high (all blocks have been allocated
at the RIR level), the fraction of addresses that respond to TCP connections on
a given port is quite low: even popular ports like 443 (use by TLS) have less
than 2\% of IPv4 hosts respond to connection requests. This leaves a large
number of hosts available to use as dark decoys. However, if a client registers
a dark decoy address that is already happens to be used by an existing host,
there will be multiple responses when the client tries to connect, and the
connection will fail. However, this failure is still limited to the registering
client, as the application only responds to the IP of the client that
registered. In IPv6, the odds of picking a legitimate host are negligible: with
a /32 prefix of IPv6, there are $2^{96}$ addresses to choose from.

@@

\FigOverview

@@

\paragraph{Mask Site Selection}

Selecting which sites to masquerade as must be done carefully to avoid censors
being able to detect obvious choices. For example, if a small university network
has a dark decoy in their network that appears to be \texttt{apple.com}, it
would be easy for a censor to block as a likely non-legitimate host. Likewise,
if a dark decoy at an IP address pretends to be a domain (\texttt{example.com}) that
globally resolves to a single different IP address, the censor could also
identify and block the dark decoy.

\smallskip
\noindent
\emph{Nearby sites} - One strategy for selecting mask sites to mimic is to pick websites that are
legitimately hosted in or near the network of the dark decoy addresses. This
effectively creates copies of legitimate sites, with the censor unable to
determine which copies are real and which are the dark decoys. However, as
mentioned, other signals such as DNS may reveal the true mask site.

\smallskip
\noindent
\emph{Alexa sites} -
An alternative strategy is to use popular sites, such as those from the Alexa
top million~\cite{alexa} list. As mentioned previously, it may be wise to avoid
sites that are obviously not hosted in the dark decoy address range, such as
large companies that run their own datacenters and own their own ASN.
The list could also be filtered to domains that resolve to different IP
addresses from different vantage points, making it harder for a censor to know
if a dark decoy corresponds to a domain's IP.

\smallskip
\noindent
\emph{Passive observation} -
The ISP tap could also collect sites by passively observing DNS requests, TLS
SNI, or certificates that pass by. This would allow for building a realistic set
of sites that are plausibly in the vicinity of the dark decoy addresses
that pass by the tap. It also has the added bonus of being able to discover
IPv6 addresses that could be used as decoys (for registration), where active
scanning would be infeasible.

In practice, clients can often try multiple dark decoys/mask sites over
several attempts, as blocking the client outright may negatively impact other
unrelated users behind the same network (e.g. in the case of NAT). Thus, even a
censor that can block most (but not all) mask site only delays access, and
doesn't prevent it outright.

@@

TLS~1.3~\cite{tls13} offers several features that may greatly simplify dark
decoy application design. For instance, TLS~1.3 handshakes include encrypted
certificates, potentially obviating the need to impersonate mask sites.
Unfortunately, TLS~1.3 currently still sends the SNI in the (plaintext) Client
Hello, meaning we would still have to choose a realistic domain to fool a
censor.

However, there are proposals to encrypt the SNI in the Client Hello~\cite{esni},
though none have been implemented or deployed as of early 2019. Nonetheless,
if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for dark
decoy applications by allowing the domain to remain hidden from the censor.
While the censor could still try to actively probe with guesses for the SNI,
servers could respond with generic ``Unknown SNI'' errors. If such responses
were common for incorrect SNI, the censor's efforts to identify dark decoys
would be frustrated.
